Pre-processing Data from Embedded Questions NoContext Corpus Study

### 2022-11-08 analysis/03_experiment/rscripts/pre-processing.Rmd
raw graphs with fourth category

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/test_overall.pdf")

agr = test %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

>>>>

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/overall_raw.pdf",width=3.5,height=3)
```

```{r}
agr = test %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

### 2022-11-08 analysis/04_experiment/rscripts/pre-processing.Rmd
raw graphs with fourth category

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/test_everything.pdf")

length(unique(test$MatrixVerb)) # 175 verbs

>>>>

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/overall_raw.pdf",width=3.5,height=3)
```

```{r}
length(unique(test$MatrixVerb)) # 175 verbs

### 2022-11-08 analysis/05_experiment/rscripts/pre-processing.Rmd
raw graphs with fourth category

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/test_everything.pdf")

>>>>

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/2a_overall_raw.pdf",width=3.5,height=3)
```

```{r]}

### 2022-11-08 analysis/06_experiment/rscripts/pre-processing.Rmd
raw graphs with fourth category

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/test_everything.pdf")

>>>>

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/2b_overall_raw.pdf",width=3.5,height=3)
```

```{r}
